% LaTeX source of my resume
% =========================

% Commented for easy reuse... ;)
% This file is licensed under the CC-NC-ND Creative Commons license.

% start a document with the here given default font size and paper size
\documentclass[10pt,a4paper]{article}

% include the `tex` instructions that takes care of loading packages and defining commands
\include{resume}

\begin{document}  % begin the content of the document
\sloppy  % this to relax whitespacing in favour of straight margins

% Contact

\maintitle{Mitja Kramberger}{Principal Engineer}  % title on top of the document
\nobreakvspace{0.3em}  % add some page break averse vertical spacing

\noindent
mitja.kramberger@gmail.com\sbull
\href{http://github.com/mkramb}{github.com/mkramb}

\spacedhrule{0.9em}{-0.4em}  % a horizontal line with some vertical spacing before and after

% Highlights

\roottitle{Highlights}

\begin{indentsection}
\item
\begin{itemize}[leftmargin=0cm]
    \item \textbf{Courage to spark change} Continuous improvement is a collective responsibility, but taking action is an individual commitment. A prime example of this is winning {\href{https://youtu.be/gdmrfGAZB0g?t=415}{a hackathon at Atlassian}} and successfully transforming the idea into a shipped product, demonstrating initiative, collaboration, and execution.
    \item \textbf{Service Orchestration} I possess in-depth expertise in AWS and Kubernetes, with a proven track record of championing the adoption of telemetry across the entire technology stack. By integrating advanced monitoring tools and practices, I have empowered teams to gain actionable insights into system performance and reliability.
    \item \textbf{SRE Culture} Enabled workflows that previously required hours to complete to run in under a minute by leveraging cloud services and optimizing build tools across the organization. Additionally, I bring valuable experience from industry-leading companies such as Atlassian and CloudBees, where I contributed to driving efficiency and innovation at scale.
\end{itemize}
\end{indentsection}

\spacedhrule{0.9em}{-0.4em} 

% Experience

\roottitle{Experience}

\headedsection
  {\href{https://froter.com/}{Forter}}
  {\textsc{London, United Kingdom}} {%

  \headedsubsection
    {Staff Engineer}
    {May \apo25 -- Present}
    {\bodytext{
        Working on payment solutions at Forter, to drive secure and frictionless commerce.
    }}
}

\headedsection
  {\href{https://primarybid.com/}{PrimaryBid}}
  {\textsc{London, United Kingdom}} {%

  \headedsubsection
    {Senior Principal Engineer}
    {Oct \apo21 -- Apr \apo25}
    {\bodytext{
        Led the rebuild of internal accounting software for subscriptions and allocations, integrating diverse allocation models in collaboration with the Data team. 
        Focused on scalability with performance testing, achieving horizontal scaling, built-in retries, enhanced observability, and documented runbooks.
    }}
}

\headedsection
  {\href{http:s//www.checkout.com}{Checkout.com}}
  {\textsc{London, United Kingdom}} {%

  \headedsubsection
    {Senior Engineering Manager}
    {May \apo20 -- Oct \apo21}
    {\bodytext{
        Overseeing the Alternative Payments orchestration layer for mobile and web clients, as well as the Payment Links product.
        Championed serverless architecture, established standards and best practices to drive engineering excellence across the department.
    }}
}

\headedsection
  {\href{http://www.photobox.com}{Photobox}}
  {\textsc{London, United Kingdom}} {%

  \headedsubsection
    {Principal Engineer}
    {Apr \apo19 -- Apr \apo20}
    {\bodytext{
      Led the implementation of the Photobox Editor experience, achieved 10x improvement in photobook service rendering times,
      reducing average processing time, delivering cost-efficient solution, by leveraging a pay-per-usage model with built-in monitoring, automated retry mechanisms, 
      and automated support runbooks.
    }}
}

\headedsection
  {\href{https://www.cloudbees.com}{Cloudbees}}
  {\textsc{London, United Kingdom}} {%
  \headedsubsection
    {Senior Engineer}
    {Jun \apo18 -- Apr \apo19}
    {\bodytext{
      Led the UI implementation for the internal product KubeCD, which has since become an official add-on for {\href{https://jenkins-x.io}{JenkinsX}}. 
      This involved designing and delivering a user-friendly interface that integrates seamlessly with JenkinsX workflows, enhancing usability and adoption across teams.
    }}
}

\headedsection
  {\href{https://www.jpmorgan.com/country/uk/en/jpmorgan}{JPMorgan Chase \& Co.}}
  {\textsc{London, United Kingdom}} {%
  \headedsubsection
    {VP Consultant}
    {Oct \apo17 -- May \apo18}
    {\bodytext{
      Provided strategic guidance on the technical direction for UX components and enhancements to our internal UI library, ensuring consistency, scalability,
      and ease of use across projects. Additionally, I authored a Kubernetes-based DevOps pipeline that streamlined the feature build process and significantly 
      simplified deployments.
    }}
}

\headedsection
  {\href{https://www.lab49.com}{Lab49}}
  {\textsc{London, United Kingdom}} {%
  \headedsubsection
    {Senior Consultant}
    {May \apo17 -- Oct \apo17}
    {\bodytext{
      Led the implementation of the internal {\href{https://www.investopedia.com/terms/m/mifid-ii.asp}{MIFID2 project}} compliance project, ensuring alignment
      with regulatory requirements and delivering a robust, scalable solution. This included collaborating with cross-functional teams to define technical requirements 
      and integrating monitoring and reporting mechanisms to meet regulatory standards.
    }}
}

\headedsection
  {\href{https://www.publicissapient.com}{Sapient Global Markets}}
  {\textsc{London, United Kingdom}} {%
  \headedsubsection
    {Manager Interactive Development}
    {Aug \apo16 -- May \apo17}
    {\bodytext{
      Authored the development of an internal web accelerator designed to assist engineers in efficiently starting new projects. This tool automated the
      provisioning of repositories, CI/CD pipelines, and provided templates tailored to various use cases, significantly reducing setup time and improving consistency.
    }}
}

\headedsection
  {\href{https://www.lloydsbank.com}{Lloyds Banking Group}}
  {\textsc{London, United Kingdom}} {%
  \headedsubsection
    {Technical Lead}
    {Apr \apo16 -- Aug \apo16}
    {\bodytext{
      Led multiple UI-focused teams, overseeing the maintenance of their build pipelines and supporting a collaborative Agile environment across the group.
      Spearheaded the creation of the Lloyds Skeleton App, which served as the foundational codebase for all UI projects, streamlining development processes and ensuring consistency.
    }}
}

\begin{center}
  \emph{Please refer to \href{http://www.linkedin.com/in/mkramb}{my Linkedin profile} for the complete list of work experiences.}
\end{center}

\end{document}
